New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/article.tex
reformulation acknowledgments

\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
us during the whole research and writing. We also would like to address warm thanks
to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
new lower bound for \(\WS(6)\).

>>>>

\qquad We would first like to thank our school CentraleSupélec and its Research Pole 005 led by Joanna Tomasik allowing us to
make this project in our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).
